\begin{thebibliography}{10}

\bibitem{Agrawal94DSBP}
H.~Agrawal.
\newblock Dominators, super block, and program coverage.
\newblock In {\em {SIGPLAN -- SIGACT} Symposium on Principles of Programming
  Languages -- {POPL'94}}, pages 25--34, Portland, Oregon, January 1994. {ACM}
  Press.

\bibitem{Agrawal98MSTA}
H.~Agrawal, J.~Alberi, J.~R. Horgan, J.~Li, S.~London, W.~E. Wong, S.~Ghosh,
  and N.~Wilde.
\newblock Mining system tests to aid software maintenance.
\newblock {\em {{IEEE} Computer}}, 31(7):64--73, July 1998.

\bibitem{JUnit02UDCA}
K.~Beck and E.~Gamma.
\newblock {JU}nit cookbook.
\newblock web page, 2002.
\newblock Available on-line: \url{http://www.junit.org/} [01-20-2003].

\bibitem{Chidamber94MSOO}
S.~R. Chidamber and C.~F. Kemerer.
\newblock A metric suite for object oriented design.
\newblock {\em {{IEEE} Transactions on Software Engineering}}, 20(6):476--493,
  June 1994.

\bibitem{Dahm01BCEB}
M.~Dahm.
\newblock Byte code engineering with the {BCEL} {API}.
\newblock Technical Report B-17-98, Freie Universit\"{a}t Berlin -- Institut
  f\"{u}r Informatik, Berlin -- German, April 2001.
\newblock Available on-line at: \url{http://bcel.sourceforge.net/}
  [04-13-2002].

\bibitem{Gammatech00DGPS}
Inc. GrammaTech.
\newblock Dependence graphs and program slicing.
\newblock White Paper, March 2000.
\newblock Available on-line: \url{http://www.grammatech.com/research/}.

\bibitem{Harrold94PDFT}
M.~J. Harrold and G.~Rothermel.
\newblock Performing data flow testing on classes.
\newblock In {\em Second ACM SIGSOFT Symposium on Foundations of Software
  Engineering}, pages 154--163, New York, NY, December 1994. ACM Press.

\bibitem{Herman76DFAA}
P.~M. Herman.
\newblock A data flow analysis approach to program testing.
\newblock {\em Australian Computer Journal}, 8(3):92--96, November 1976.

\bibitem{Horgan91DFCC}
J.~R. Horgan and S.~A. London.
\newblock Data flow coverage and the {C} language.
\newblock In {\em Symposium Software Testing, Analysis, and Verification},
  pages 87--97, Victoria, British Columbia, Canada, October 1991. ACM Press.

\bibitem{Ilog03JVIE}
{ILOG, Inc}.
\newblock Ilog jviews component suite.
\newblock web page, 2003.
\newblock \url{http://www.ilog.com/products/jviews/}.

\bibitem{Lindholm99JVMS}
T.~Lindholm and F.~Yellin.
\newblock {\em The {J}ava Virtual Machine Specification}.
\newblock Addison-Wesley, 2 edition, 1999.

\bibitem{Lorenz94OOSM}
M.~Lorenz and J.~Kidd.
\newblock {\em Object-Oriented Software Metrics: A Practical Guide}.
\newblock Prentice Hall, Englewood Cliffs, New Jersey, 1994.
\newblock Object-Oriented Series.

\bibitem{Maldonado91CPUC-EN}
J.~C. Maldonado.
\newblock {\em Potential-Uses Criteria: A Contribution to the Structural
  Testing of Software}.
\newblock Doctoral dissertation, DCA/FEE/UNICAMP, Campinas, SP, Brazil, July
  1991.
\newblock (in Portuguese).

\bibitem{McCabe76CMEA}
T.~McCabe.
\newblock A complexity measure.
\newblock {\em {{IEEE} Transactions on Software Engineering}}, 2(4):308--320,
  December 1976.

\bibitem{Orso01UCMS}
A.~Orso, M.~J. Harrold, D.~Rosenblum, G.~Rothermel, H.~Do, and M.~L. Soffa.
\newblock Using component metacontent to support the regression testing of
  component-based software.
\newblock In {\em IEEE International Conference on Software Maintenance
  (ICSM'01)}, pages 716--725, Florence, Italy, November 2001. {IEEE} Computer
  Society Press.

\bibitem{Piwowarski93CMED}
P.~Piwowarski, M.~Ohba, and J.~Caruso.
\newblock ``{C}overage measurement experience during function test''.
\newblock In {\em Proceedings of the 15th International Conference on Software
  Engineering}, pages 287--301, Baltimore, MD, May 1993.

\bibitem{Pressman00SEPA}
R.~S. Pressman.
\newblock {\em Software Engineering -- A Practitioner's Approach}.
\newblock McGraw-Hill, 5 edition, 2000.

\bibitem{Rainsberger03JSGU}
J.~B. Rainsberger.
\newblock {JU}nit: A starter guide.
\newblock Web Page, 2003.
\newblock Available on-line:
  \url{http://www.diasparsoftware.com/articles/JUnit/jUnitStarterGuide.html}.

\bibitem{Rapps85SSTD}
S.~Rapps and E.~J. Weyuker.
\newblock Selecting software test data using data flow information.
\newblock {\em {{IEEE} Transactions on Software Engineering}}, 11(4):367--375,
  April 1985.

\bibitem{Roper94STES}
M.~Roper.
\newblock {\em Software Testing}.
\newblock McGrall Hill, 1994.

\bibitem{Sinha98APEH}
S.~Sinha and M.~J. Harrold.
\newblock Analysis of programs with exception-handling constructs.
\newblock In {\em ICSM'98 -- International Conference on Software Maintenance},
  pages 348--357, Bethesda, MD, November 1998.

\bibitem{Sinha99CTEH}
S.~Sinha and M.~J. Harrold.
\newblock Criteria for testing exception-handling constructs in {J}ava
  programs.
\newblock In {\em International Conference on Software Maintenance}, pages
  265--274, Oxford, England, August 1999. {IEEE} Computer Society Press.

\bibitem{Tip95SPST}
F.~Tip.
\newblock A survey of program slicing techniques.
\newblock {\em Journal of Programming Languages}, 3:121--189, 1995.

\bibitem{Utsonomia02EAMS}
C.~T. Utsonomia.
\newblock Estudo e aplica\c cão de m\'etricas para sistemas orientados a
  objeto.
\newblock Exame geral de qualificação, Universidade Estadual do Parana,
  Departamento de Informática, Curitiba, PR, August 2002.

\bibitem{Vergilio97CRCA}
S.~R. Vergilio.
\newblock {\em Critérios Restritos: Uma Contribuição para Aprimorar a Eficácia
  da Atividade de Teste de Software}.
\newblock PhD thesis, DCA/FEEC/UNICAMP, Campinas, SP, July 1997.

\bibitem{Vincenzi03STOO}
A.~M. Vincenzi, W.~E. Wong, M.~E. Delamaro, A.~S. Simão, and J.~C. Maldonado.
\newblock Structural testing of object-oriented programs.
\newblock Technical report, ICMC/USP, 2003.
\newblock (in preparation).

\bibitem{Vincenzi03JBSD}
A.~M.~R. Vincenzi, M.~E. Delamaro, J.~C. Maldonado, and W.~E. Wong.
\newblock Java bytecode static analysis: Deriving structural testing
  requirements.
\newblock In {\em 2nd {UK} Software Testing Workshop -- UK-Softest'2003},
  pages~--, Department of Computer Science, University of York, York, England,
  September 2003. University of York Press.
\newblock (accepted for publication).

\bibitem{Weiser79PSFP}
M.~Weiser.
\newblock {\em Program Slicing: Formal, Psychological and Practical
  Investigations of an Automatic Program Abstraction Method}.
\newblock Phd thesis, The University of Michigan, Ann Arbor , Michigan, 1979.

\bibitem{Weiser82PUSW}
M.~Weiser.
\newblock Programmers use slices when debugging.
\newblock {\em Communications of the ACM}, 25(7):446--452, 1982.

\bibitem{Weiser84PSLI}
M.~Weiser.
\newblock Program slicing.
\newblock {\em {{IEEE} Transactions on Software Engineering}}, 10(4):352--357,
  July 1984.

\bibitem{Wong94ETSS}
W.~E. Wong, J.~R. Horgan, S.~London, and A.~P. Mathur.
\newblock Effect of test set size and block coverage on fault detection
  effectiveness.
\newblock In {\em Fifth IEEE International Symposium on Software Reliability
  Engineering}, pages 230--238, Monterey, CA, November 1994.

\bibitem{Wong98ETSM}
W.~E. Wong, J.~R. Horgan, S.~London, and A.~P. Mathur.
\newblock ``{E}ffect of test set minimization on fault detection
  effectiveness''.
\newblock {\em Software-Practice and Experience}, 28(4):347--369, April 1998.

\bibitem{Zhao99ACFJ}
J.~Zhao.
\newblock Analyzing control flow in {J}ava bytecode.
\newblock In {\em 16th Conference of Japan Society for Software Science and
  Technology}, pages 313--316, September 1999.

\bibitem{Zhao00DAJB}
J.~Zhao.
\newblock Dependence analysis of {J}ava bytecode.
\newblock In {\em 24th IEEE Annual International Computer Software and
  Applications Conference (COMPSAC'2000)}, pages 486--491, Taipei, Taiwan,
  October 2000. {IEEE} Computer Society Press.

\end{thebibliography}
